Sailing the High Seas:\\ A Christian Exploration of Piracy

### 2024-04-09 paper.tex
Reformat displayquore

\begin{displayquote}
  \textins That ideas should freely spread from one to another over the globe, for the
    moral and mutual instruction of man, and improvement of his condition, seems to have been
    peculiarly and benevolently designed by nature, when she made them, like fire, expansible
    over all space, without lessening their density at any point, and like the air in which we
    breathe, move, and have our physical being, incapable of confinement or exclusive
    appropriation. Inventions then cannot, in nature, be a subject of property.  Thomas
    Jefferson ~\cite{barlow:wine}
\end{displayquote}
It is generally accepted that piracy is an illegal activity, but what is often overlooked
is the legitimate role that piracy plays in a variety of contexts. When it comes to
subverting oppressive regimes, for instance, the tools that piracy provides are
indispensable and for protecting the interests of consumers from predatory business
practices, the abilities of piracy are unmatched. Needless to say, with every unregulated
system comes abuse and piracy is no exception. As a Christian, how should one approach
such a tool and how can it be utilized for the betterment of God's kingdom? In the paper
that follows, piracy will be analyzed through a number of lenses, culminating in a
Christian response to this issue. In doing so, the hope is that the reader attains a
fresh, wholistic understanding of the potential value of piracy.
% explain the definition of piracy that we're using for this paper:
% it's not just the act of downloading copyrighted content but it includes the tools that
% are used to accomplish this task.

>>>>

\begin{displayquote}
  \textins{T}hat ideas should freely spread from one to another over the globe,
  for the moral and mutual instruction of man, and improvement of his
  condition, seems to have been peculiarly and benevolently designed by nature,
  when she made them, like fire, expansible over all space, without lessening
  their density at any point, and like the air in which we breathe, move, and
  have our physical being, incapable of confinement or exclusive appropriation.
  Inventions then cannot, in nature, be a subject of property.
  Thomas Jefferson~\cite{barlow:wine}
\end{displayquote}
It is generally accepted that piracy is an illegal activity, but what is often overlooked
is the legitimate role that piracy plays in a variety of contexts. When it comes to
subverting oppressive regimes, for instance, the tools that piracy provides are
indispensable and for protecting the interests of consumers from predatory business
practices, the abilities of piracy are unmatched. Needless to say, with every unregulated
system comes abuse and piracy is no exception. As a Christian, how should one approach
such a tool and how can it be utilized for the betterment of God's kingdom? In the paper
that follows, piracy will be analyzed through a number of lenses, culminating in a
Christian response to this issue. In doing so, the hope is that the reader attains a
fresh, wholistic understanding of the potential value of piracy.
% explain the definition of piracy that we're using for this paper:
% it's not just the act of downloading copyrighted content but it includes the tools that
% are used to accomplish this task.
